Can We Crunch the Social Graph on the Cheap?

### 2011-01-25 doc/hotpar2011/softxmt-hotpar2011.tex
fixed authors

%\numberofauthors{7}
%\author{
%Jacob Nelson, Brandon Myers, Andrew Hunter, Dan Grossman, Mark Oskin,
%Carl Ebeling, Luis Ceze\\
%University of Washington\\
%\email{\{nelson, bdmyers, ahh, djg, oskin, ebelin, luisceze\}@cs.washington.edu}\\ \\
%Simon Kahan \\ 
%Pacific Northwest National Lab\\
%\email{skahan@cs.washington.edu}\\ \\
%Preston Briggs\\ 
%Cray Inc.\\
%\email{preston.briggs@gmail.com}\\
%}
\authorinfo{Mr Nobody}{University of Washington}{nobody.cs.washington.edu}

>>>>

%\numberofauthors{7}
%\author{
%Jacob Nelson, Brandon Myers, Andrew Hunter, Dan Grossman, Mark Oskin,
%Carl Ebeling, Luis Ceze\\
%University of Washington\\
%\email{\{nelson, bdmyers, ahh, djg, oskin, ebelin, luisceze\}@cs.washington.edu}\\ \\
%Simon Kahan \\ 
%Pacific Northwest National Lab\\
%\email{skahan@cs.washington.edu}\\ \\
%Preston Briggs\\ 
%Cray Inc.\\
%\email{preston.briggs@gmail.com}\\
%}

%todo format the UW names horizontally
\authorinfo{Jacob Nelson, Brandon Myers, Andrew Hunter, Dan Grossman, Mark Oskin,
Carl Ebeling, Luis Ceze}{University of Washington}{\{nelson, bdmyers, ahh, djg, oskin, ebelin, luisceze\}@cs.washington.edu}
\authorinfo{Simon Kahan}{Pacific Northwest National Lab}{skahan@cs.washington.edu}
\authorinfo{Preston Briggs}{Cray Inc.}{preston.briggs@gmail.com}
